title: "Predict Citibike"
author: "Alexandra Roffe (Yeshiva University)"
date: '6/17/2022'
---
  
  ```{r setup, include=FALSE}
library(scales)
library(tidyverse)
library(modelr)
library(broom)

theme_set(theme_bw())
options(repr.plot.width=4, repr.plot.height=3)
```

# Write a new file called test_citibike_predictions.Rmd that loads in the 2015 trips_2015.Rdata file and weather data along with your saved model (from yesterday's .Rdata file, and predicts the number of trips for each day.

```{r}
load("trips_2015.RData")
load("bestmodel.RData")

```


# join weather and the data 
```{r}
test_2015 <- full_join(trips, weather) # by "ymd"
# add a num_trips
test_2015 <- test_2015 %>%
  group_by(ymd) %>%
  mutate(num_trips = n())
```


```{r}
trips_per_day = read_tsv('trips_per_day.tsv')
library(lubridate)

trips_per_day <- trips_per_day %>% 
  mutate(day_of_week = wday(ymd)) %>%
  mutate(weekday_or_weekend = as.integer(day_of_week > 1 & day_of_week < 7)) %>% # 1 and 7 are weekends. 
  mutate(prcp2 = as.integer(prcp > 0.7))

test_2015 <- test_2015 %>% 
  mutate(day_of_week = wday(ymd)) %>%
  mutate(weekday_or_weekend = as.integer(day_of_week > 1 & day_of_week < 7)) %>% # 1 and 7 are weekends. 
  mutate(prcp2 = as.integer(prcp > 0.7))
```

# Adding holidays
```{r}
holidays = read_csv('holidays.csv', c('row_number', 'ymd', 'title'))

trips_per_day <- left_join(trips_per_day, holidays, "ymd") %>%
  mutate(holiday = is.na(title)) %>%
  mutate(holiday1 = as.integer(holiday))

test_2015 <- left_join(test_2015, holidays, "ymd") %>%
  mutate(holiday = is.na(title)) %>%
  mutate(holiday1 = as.integer(holiday))